Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Update main.tex
format template
Soft prompting

\documentclass{article}

@@

@@

Hard prompts (discrete words of natural language) are opposed to soft prompts (learnable continuous representations).

@@

\paragraph{Metrics}

>>>>

\documentclass[10pt]{article}
\usepackage[a4paper, margin=1.25in]{geometry}

@@

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{*0.8}{*0.8}

@@

Soft prompting is an alternative to fine-tuning where the model is frozen while only a small number of "soft" prompt parameters are trained \cite{lester2021prompt}. These parameters are used to guide the model in the right direction.

@@

\paragraph{Metrics}
We'll evaluate model's performance with question answering accuracy domain-wise in order to have a fair comparison with leaderboards.
